Canada’s Battle Against Car Theft: Progress Amid Persistent Challenges 

### 2024-11-26 paper/paper.qmd
minorchange1.3
minorchange1.x is used to update title, structure and introduction.

---
title: "Canada’s Battle Against Car Theft: Progress Amid Persistent Challenges "
subtitle: "Government measures and public vigilance show promise, but organized theft networks remain a concern."
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Canada’s Battle Against Car Theft: Progress Amid Persistent Challenges "
subtitle: "Government measures and public vigilance show promise, but organized theft networks remain a concern."
author: 
  - Yiyue Deng
thanks: "Code and data are available at: [https://github.com/vanessadyy/Car_Theft](https://github.com/vanessadyy/Car_Theft)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
